Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-11 Latex/journal_v1/V5/pr.tex
code generation for figure 1

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_r}^2.
\end{equation}
Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
\end{equation}
Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
\begin{equation}
T_{tot} \approx T_{process}
\end{equation}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
\end{split}
\end{equation}
Where $M_s^{d}$, $M_s^{c}$ and 
$M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms.

>>>>

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_r}^2.
Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
T_{tot} \approx T_{process}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\
Where $M_s^{d}$, $M_s^{c}$ and 
$M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_s^d$, $1/\mu_s^c$ and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

In this section, numerical results for the problem are depicted to evaluate the performance of the algorithms. We consider three network slice, one for eMBB, and two another for URLLC and mMtc.
Assume we have six 4-antenna O-RU (MISO), are located in a cell with a diameter of 500 meters. We consider 20 PRB
in the network.
The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB and URLLC is $\lambda  = 300KHz$ and for mMTC $\lambda  = 600KHz$. 
The other parameters of this simulations are depicted in Table \ref{table:1a}.
\begin{table}
 \caption {Simulation Parameter} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Parameter & Value \\ [0.5ex]
  \hline\hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 120 KHz \\
  \hline
 Maximum transmit Power of each O-RU & 38dBm \\
  \hline
  Minimum delay for eMBB and mMTC &  4msec \\
  \hline
    Minimum delay for URLLC &  1msec \\
  \hline
  Minimum delay for mMTC &  7msec \\
  \hline
  Maximum fronthaul capacity  & 200 bits/sec/Hz \\
   \hline
  Minimum data rate for eMBB &  30 bits/sec/Hz \\ 
  \hline
   Minimum data rate for URLLC and mMTC &  10 bits/sec/Hz \\ 
  \hline
   Maximum received power for mMTC &  20 dBM \\ [.5ex]   
  \hline
    Maximum received power for eMBB and URLLC &  33 dBM \\ [.5ex]   
  \hline
 \end{tabular}
 \end{center}
 \end{table}
 The performance of the method is compared by two different method. The first one is a baseline scheme, which used random PRB allocation and the asociation of O-RU is based on the distance ,and channel quality, and fronthaul capacity, also the number of activated VNF for each slice is fixed. The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power is dynamically allocated, the number of VNFs are fixed and the UEs are associated to O-RU based on the quality of their channels, the fronthaul capacity, and channel distance and quality.
In Fig the aggregated throughput is demonstrated versus different number of UEs in each slice for these three methods. Here we assume that slices have the same priority.
